A Continuous Occlusion Model for Road Scene Understanding

### 2016-01-25 CVPR16/Rebuttal2/Source/contBBoxModel.tex
draft rebuttal

\subsubsection{Continuous bounding box energy with occlusion}

Object detection is usually followed by non-maximal suppression that results in discarding similar bounding boxes. When we are jointly optimizing detections with other cues, it is not usually desirable to go with a single bounding box. To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussians-like logistic functions. In particular, let 2D bounding box $\bb{i}$ be parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$. We fit a parametric function to the detection scores, of the form
\begin{equation}
S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \Lambda_k^{-1} \bepsilon_k^{i}(t) \right)
\end{equation}
where $A_k$ is an amplitude and $\bepsilon_k^{i}(t) = \bb{i}-\mu^{k}_d$, with $\mu^{k}_d$ the mean and $\Lambda_k$ the covariance.
%% %
%% \begin{multline}
%%   S(\bb{i}) = \\
%%   \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
%%   (\bb{i}-\mu^{(d)}_k))
%% \end{multline}
%% %
%% to detection scores, by 
We use a non-linear solver to minimize the above, with initialization from non-maximal suppressed outputs. The optimization is constrained by the symmetry and positive definiteness of $\Lambda_k^{-1}$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
%Here $\mu^{(d)}_j$ is one of the $k$ modes as a 4D vector representing a single bounding box as $[\minx, \miny, \maxx, \maxy]^\top$. The optimization is constrained with symmetry and positive definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.

>>>>

\vspace{-0.3cm}
\paragraph{Continuous bounding box energy with occlusion}
Object detection is usually followed by non-maximal suppression that results in discarding similar bounding boxes. When we are jointly optimizing detections with other cues, it is not usually desirable to go with a single bounding box. To retain the entire detection output while maintaining the continuous form of our energies, we approximate the distribution of detection scores with a multi-modal sum of Gaussians-like logistic functions. In particular, let 2D bounding box $\bb{i}$ be parameterized as a 4D vector $[\minx, \miny, \maxx, \maxy]^\top$. We fit a parametric function to the detection scores, of the form
\begin{equation}
S(\bb{i}) = \sum_k A_k \exp \left( -\bepsilon_k^{i}(t)^\top \Lambda_k^{-1} \bepsilon_k^{i}(t) \right)
\end{equation}
where $A_k$ is an amplitude and $\bepsilon_k^{i}(t) = \bb{i}-\mu^{k}_d$, with $\mu^{k}_d$ the mean and $\Lambda_k$ the covariance.
%% %
%% \begin{multline}
%%   S(\bb{i}) = \\
%%   \sum_k A_k \exp(-(\bb{i}-\mu^{(d)}_k)^\top \Sigma^{(d)-1}_k
%%   (\bb{i}-\mu^{(d)}_k))
%% \end{multline}
%% %
%% to detection scores, by 
We use a non-linear solver to minimize the above, with initialization from non-maximal suppressed outputs. The optimization is constrained by the symmetry and positive definiteness of $\Lambda_k^{-1}$, $\maxx \ge \minx$ and $\maxy \ge \miny$.
%Here $\mu^{(d)}_j$ is one of the $k$ modes as a 4D vector representing a single bounding box as $[\minx, \miny, \maxx, \maxy]^\top$. The optimization is constrained with symmetry and positive definiteness of $\Sigma^{(d)-1}_k$, $\maxx \ge \minx$ and $\maxy \ge \miny$.

### 2016-01-25 CVPR16/Rebuttal2/Source/discussions.tex
draft rebuttal

We have presented a continuous model for occlusion modeling in 3D. A key advantage is its physically-inspired modeling that lends flexibility towards occlusion reasoning for various elements of scene understanding, such as point tracks, object detection bounding boxes and scores. We demonstrate unified modeling for different applications such as point tracks associations and 3D localization. Our occlusion model can uniformly handle static and dynamic objects, which is an advantage over motion segmentation methods for point-object association. A challenge is that inference for 3D localization is currently slow, requiring a few minutes per window of frames, which prevents exhaustive cross-validation for tuning of weights. Our future work will explore speeding up the inference, for example, by approximating the graph with a tree using the Chow-Liu method \cite{chow1968approximating}, allowing belief propagation for fast inference.

>>>>

We have presented a theoretically novel continuous model for occlusion reasoning in 3D. A key advantage is its physical inspiration that lends flexibility towards occlusion reasoning for varied elements of scene understanding, such as point tracks, object detection bounding boxes and detection scores. We demonstrate unified modeling for different applications such as point tracks associations and 3D localization. Our occlusion model can uniformly handle static and dynamic objects, which is an advantage over motion segmentation methods for point-object association. A challenge is that inference for 3D localization is currently slow, requiring a few minutes per window of frames, which prevents exhaustive cross-validation for tuning of weights. Our future work will explore speeding up the inference, for example, by approximating the graph with a tree using the Chow-Liu method \cite{chow1968approximating}, allowing belief propagation for fast inference.

### 2016-01-25 CVPR16/Rebuttal2/Source/experiments.tex
draft rebuttal

For each sequence of the KITTI dataset, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used respectively for computing detection bounding boxes and object tracklets. We then apply \cite{Zach2007} on object tracklets to extract point tracks. From these point tracks, we create four different sets of input point tracks, namely all point tracks, occluded point tracks, dynamic point tracks and dynamic and occluded point tracks, to examine various aspects of the methods (our method focuses on occlusion scenes while RAS and BM favour dynamic scenes). In addition to point tracks, the parameters of all TPs estimated by the method~\cite{Song_Chandraker_2014} are provided to our method (for computing association probability) and the baseline method (for depth ordering).

>>>>

For each sequence of the KITTI dataset, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used respectively for computing detection bounding boxes and object tracklets. We then apply \cite{Zach2007} on object tracklets to extract point tracks. From these point tracks, we create four different sets of input point tracks, namely all point tracks, occluded point tracks, dynamic point tracks and dynamic and occluded point tracks, to examine various aspects of the methods (our method focuses on occlusion scenes while RAS and BM favour dynamic scenes). In addition to point tracks, the parameters of all objects estimated by the method of \cite{Song_Chandraker_2015} are provided to our method (for computing association probability) and the baseline method (for depth ordering).

### 2016-01-25 CVPR16/Rebuttal2/Source/experiments2.tex
draft rebuttal

\subsection{Association Experiments}
\vspace{-0.2cm}
\paragraph{Setup}
We first perform the association experiment that compares the accuracy of point-to-object association using our proposed model against a heuristic baseline and state-of-the-art motion segmentation methods. The detection bounding box baseline method (BBox) is as described at the end of Section \ref{sec:association}. For motion segmentation, we use robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity (BM)~\cite{Brox_Malik_2010}.

@@

For each sequence of the KITTI dataset, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used for computing detection bounding boxes and object tracklets, respectively. We then apply \cite{Zach2007} to extract point tracks. Note that our method can handle occlusions in both static and dynamic scenes, but motion segmentation focuses on dynamic scenes. For a complete evaluation, we create organize the point tracks into four sets: all point tracks, occluded point tracks, dynamic point tracks and dynamic as well as occluded point tracks. In addition to point tracks, the parameters of all objects (cars) estimated by the method of \cite{Song_Chandraker_2015} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).

@@

\subsection{Localization Experiments}
We report errors in translation error and dimension estimates, measured in meters per car, in Table~\ref{tab:localizationExperiment}. We compare four combinations of energies.  The energy $\EnergyTrackNoOcc$ represents the point tracks energy without accounting for occlusion, that is, we model $\EnergyTrack$ in the absence of $\Ptransmission$. Similarly, $\EnergyBBoxNoOcc$ is the energy without the modification of $\Lambda_k$ that accounts for occlusion. The results show that the use of continuous occlusion model improves the localization accuracy in terms of the translation error, which is he most significant metric affected by all cues. Occlusion modeling for point tracks is always beneficial, while that for detection improves localization, but penalizes dimension since we explicitly allow greater uncertainty in occluded edges of the bounding box. Note that none of our energies optimize yaw angles for static objects, which can be handled in practice through either the detector orientation or external information such as lane geometry.

>>>>

\subsection{Association Experiments}
%\vspace{-0.2cm}
\paragraph{Setup}
We first perform the association experiment that compares the accuracy of point-to-object association using our proposed model against a heuristic baseline and state-of-the-art motion segmentation methods. The detection bounding box baseline method (BBox) is as described at the end of Section \ref{sec:association}. For motion segmentation, we use robust algebraic segmentation with hybrid perspective constraints (RAS)~\cite{Rao_etal_2010} and spectral clustering with point track spatial affinity (BM)~\cite{Brox_Malik_2010}.

@@

For each sequence of the KITTI dataset, the methods of \cite{Felzenszwalb_etal_2010} and \cite{Choi_Savarese_2010} are used for computing detection bounding boxes and object tracklets, respectively. We then apply \cite{Zach2007} to extract point tracks. Note that our method can handle occlusions in both static and dynamic scenes, but motion segmentation focuses on dynamic scenes. For a complete evaluation, we organize the point tracks into four sets: all point tracks, occluded point tracks, dynamic point tracks and dynamic as well as occluded point tracks. In addition to point tracks, the parameters of all objects (cars) estimated by the method of \cite{Song_Chandraker_2015} are provided to our method (for computing association probability) and the baseline BBox method (for depth ordering).

@@

\subsection{Localization Experiments}
We report errors in translation and dimension estimates, measured in meters per car, in Table~\ref{tab:localizationExperiment}. Average depth of cars in the dataset is approximately $20$ meters. We compare four combinations of energies.  The energy $\EnergyTrackNoOcc$ represents the point tracks energy without accounting for occlusion, that is, we model $\EnergyTrack$ in the absence of $a^{ij} (\lambda)$. Similarly, $\EnergyBBoxNoOcc$ is the energy without the modification of $\Lambda_k$ that accounts for occlusion. We observe that the use of the continuous occlusion model improves the localization accuracy in terms of the translation error, which is the most significant metric affected by all cues. Occlusion modeling for detection increases dimension error since we explicitly allow greater uncertainty in occluded edges of the bounding box. Note that none of our energies optimize yaw angles for static objects, which can be handled in practice through either the detector orientation or external information such as lane geometry.
